---
title: "lab6"
author: "Margaret Hammond"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based test

We'll make our own samples using a pseudorandom generator.

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)
# through set.seed, we all have the same random sample

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

## Histogram

```{r}
hist(gp_1)

hist(gp_2)
```

Try a t-test:
```{r}
t.test(gp_1, gp_2)
```

What is the meaning of the p-value?
There is a 19% chance that from these populations, we would randomly select the same difference. (my guess)

#### Correct Definition
**If the samples are pulled from the populations with the same mean, there is a 19% chance that we will find sample means at least as different as ours by random chance.**
If these samples were drawn from populations with the same mean, the probability of taking two random samples with means *at least as different* as the sample means we found by random chance (taking into account spread, n) which is 19.8%
We would accept the null hypot. 
Retain (fail to reject) the null hypothesis.

Warning: people get weirdly upset if you say "accept" the null. 

```{r}
mwu <- wilcox.test(gp_1, gp_2)

mwu
```

What the p value means
If the samples are pulled from the populations with the same ranks of values (medians), the probability of finding two samples with ranks *at least as different* as those in our samples is 0.28.

There is no significant difference in ranks (often you'll see medians) between group 1 and group 2. 

Median scores for group 1 (M = 14) and group 2 (M = 12) did not differ significantly (Mann Whitney U test: U(df) = 86, p = 0.28)

## Linear Regression

Simple linear regression (single dependent variable, a single independent variable)

```{r}
# Make an exploratory plot of penguin body mass vs. flipper length (x-axis)

ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) + 
  geom_point() +
  geom_smooth(method = "lm") #lm stands for linear model
```

Find a linear regression model using ordinary least squares describing the relationship between flipper length and body mass for these penguins.

3 pieces:

- What type of model?
- What is the relationship to model (DV ~ IV(s))
- Where is the data that's used to create this model?

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)

# y = mx + b
# body mass = flipper length*(something) + something
# body mass = flipper length * 49.69 - 5780.83
# for every 1 mm increase for flipper length, I expect 49.7 g increase of body mass.
# 49.69 g/mm
# -5780.8 g. The y-intercept. 
```

### broom package returns model outputs as tidy data frames

```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

penguin_lm_tidy

glance(penguin_lm)

```

How can I actually include my model equation in a report?

```{r}
ex1 <- extract_eq(model = penguin_lm, use_coefs = TRUE)

ex1


```

```{r}
plot(penguin_lm)

# This creates 4 plots, all to show us the residuals and the normalcy. 
# Residuals vs Fitted, Normal Q-Q, Scale-Location, Residuals vs Leverage. I should probably look into these more cuz I could stand to understand them better. 
#heterosedastic. The variance residuals change throughout the model. 
```

